A hazards approach to the biometric analysis of infant mortality

### 2023-03-30 Slides/slides.Rmd
finish

@@

axis(2, las = 1)
abline(h = 0, v = c(0, 365))
axis(1, at = g(c(d, 365)), labels = c(d, 365))
tabb <- g(c(0, 28, 41, 90,120, 180, 309, 365))
##axis(3, at = tabb, labels = round(tabb))
box()
abline(v = g(28), lty = 2, col = "magenta")
##text(g(12), 0.08, "Neonatal", col = "red")
text(g(130), 0.11, "Total")
text(g(130), 0.02, "Exogenous", col = "blue")
text(g(130), 0.06, "Endogenous", col = "red")
ttt <- sum(g(c(41, 90, 120, 180, 319) - 28)) + 90 * (g(365) - g(28))
lambda <- 5 / ttt
x <- g(0:365)
y <- Hweibull(x, shape = 1, scale = 1 / lambda)
lines(x, y, lty = 2, col = "blue")
axis(4, at = c(0, y[366], h[10]), labels = round(c(0, y[366], h[10]), 3), las = 1)
lines(c(365, 365), c(0, y[366]), col = "blue", lwd = 3)
lines(c(365, 365), c(y[366], h[10]), col = "red", lwd = 3)
text(30, 0.12, "Neonatal", col = "red", cex = 0.8)
text(110, 0.12, "Post-neonatal", col = "blue", cex = 0.8)
## Add neonatal:
xn <- g(d)
yn <- h - Hweibull(xn, shape = 1, scale = 1 / lambda)
lines(xn, yn, type = "l", col = "red", lty = 4)
```

@@

*   Knodel \& Kintner (1977) 
*   Wrigley (1977).
*   Lynch, Greenhouse \& Brändström (1998).
*   Bengtsson (1999).
*   Manfredini (2004).

@@

## Comparison

@@

>>>>

\tiny

@@

axis(2, las = 1)
abline(h = 0, v = c(0, 365))
axis(1, at = g(c(d, 365)), labels = c(d, 365))
tabb <- g(c(0, 28, 41, 90,120, 180, 309, 365))
##axis(3, at = tabb, labels = round(tabb))
box()
abline(v = g(28), lty = 2, col = "magenta")
##text(g(12), 0.08, "Neonatal", col = "red")
text(g(130), 0.11, "Total")
text(g(130), 0.02, "Exogenous", col = "blue")
text(g(130), 0.06, "Endogenous", col = "red")
ttt <- sum(g(c(41, 90, 120, 180, 319) - 28)) + 90 * (g(365) - g(28))
lambda <- 5 / ttt
x <- g(0:365)
y <- Hweibull(x, shape = 1, scale = 1 / lambda)
lines(x, y, lty = 2, col = "blue")
axis(4, at = c(0, y[366], h[10]), labels = round(c(0, y[366], h[10]), 3), las = 1)
lines(c(365, 365), c(0, y[366]), col = "blue", lwd = 3)
lines(c(365, 365), c(y[366], h[10]), col = "red", lwd = 3)
text(30, 0.12, "Neonatal", col = "red", cex = 0.8)
text(110, 0.12, "Post-neonatal", col = "blue", cex = 0.8)
## Add endogenous:
xn <- g(d)
yn <- h - Hweibull(xn, shape = 1, scale = 1 / lambda)
lines(xn, yn, type = "l", col = "red", lty = 4)
lines(c(g(28), g(309)), c(yn[6], yn[6]), lty = 4, lwd = 1)
```

@@

*   Knodel \& Kintner (1977).
    *    Discusses effects of breastfeeding habits.
*   Wrigley (1977).
    *    Problems with data recording.
*   Lynch, Greenhouse \& Brändström (1998).
    *    Mentions "constant hazard".
    *    Suggest linear regression methods.
*   Bengtsson (1999).
    *    Data quality.
*   Manfredini (2004).
    *    Deals with effect of climate variation.

@@

## Cohort effect of birth month, Västerbotten

\begin{columns}
\begin{column}{0.6\textwidth}

\includegraphics[width=0.8\textwidth,height=0.7\textheight]{../paper2_files/figure-latex/plotcohort-1.pdf}

\begin{column}{0.4\textwidth}

Conclusion:
\vspace{2\baselineskip}

Post-neonatal linearity is a population property, not an individual.
\end{column}

## Period effect of month, Västerbotten

\begin{columns}

\begin{column}{0.6\textwidth}

\includegraphics[width=0.8\textwidth,height=0.7\textheight]{../paper2_files/figure-latex/plotcohort3-1.pdf}

\begin{column}{0.4\textwidth}

Looks quite proportional!

<!--
## Comparison

@@

-->
